---
title: "Facebook Photo Analysis"
author: "Craig R. McClain"
date: "11/18/2018"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages Needed

```{r, warning=FALSE, message=FALSE}
require(ggplot2)
require(dplyr)
library(chron)
library(gridExtra)
require(DescTools)
library(car)
library(scales)
require(corrplot)
library(Hmisc)
library(plyr)
library(AER)
library(MASS)
library(rcompanion)
library(multcompView)
library(emmeans)
library(pscl)
library(knitr)
library(kableExtra)
```

##Load and Process Data
```{r}
setwd("~/Desktop/Facebook Paper/Facebook Experiment")
fb_photo<-read.csv("taxa_experiment.csv", header=TRUE)
glimpse(fb_photo)
```
```{r}
fb_data <- fb_photo %>%
  mutate(Date = as.Date(Date , "%m/%d/%y"),
         Time = chron(times = Time),
         Days = as.numeric(Date-min(Date)),
         LogLikes = log10(Like.24),
         LogShares = log10(Share.24),
         LogComments = log10(Comment.24),
         LogCapCount = log10(Word.Count),
         Percent.Likes = Like.24/Like.Current,
         Percent.Comment = Comment.24/Comment.Current,
         Percent.Share = Share.24/Share.Current
  )

fb_data$Taxa <- revalue(fb_data$Taxa, c("Jellyfish"="Medusozoa", "Coral" = "Anthozoa","Gastropod  Non nudibranch  & Bivalve"="GastropodBivalve"))

glimpse(fb_data)
   
```

## Color Pallettes

Likes #3b5998 
Shares #5B9A9B
Comments #BDBC89

## Correlations Between Old and New Data


```{r, warning=FALSE, message=FALSE}
l1<- ggplot(fb_data, aes(x=log10(Like.24), y=log10(Like.Current)))+
  geom_point(pch=21, size=3, fill="#3b5998", color="black", alpha=.8)+
  geom_abline(intercept=0, slope=1)+
  geom_abline(intercept=.1, slope=1, linetype=2)+
  xlab("Log10 Likes at 24 hrs")+
  ylab("Log10 Likes Current")+
  ggtitle("A")+
  theme_bw(base_size=10)+
  theme(axis.line = element_line(colour = "darkgrey"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        legend.position="none",
        plot.title = element_text(lineheight=.8, face="bold", hjust = 0))



c1 <- ggplot(fb_data, aes(x=log10(Comment.24), y=log10(Comment.Current)))+
  geom_jitter(pch=21, size=3, fill="#BDBC89", color="black", 
              alpha=.8, width = 0.02)+
  geom_abline(intercept=0, slope=1)+
  geom_abline(intercept=.1, slope=1, linetype=2)+
  xlab("Log10 Comments at 24 hrs")+
  ylab("Log10 Comments Current")+
  ggtitle("B")+
  theme_bw(base_size=10)+
  theme(axis.line = element_line(colour = "darkgrey"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        legend.position="none",
        plot.title = element_text(lineheight=.8, face="bold", hjust = 0))

s1 <- ggplot(fb_data, aes(x=log10(Share.24), y=log10(Share.Current)))+
  geom_jitter(pch=21, size=3, fill="#5B9A9B", color="black", 
              alpha=.8, width = 0.02)+
  geom_abline(intercept=0, slope=1)+
  geom_abline(intercept=.1, slope=1, linetype=2)+
  xlab("Log10 Shares at 24 hrs")+
  ylab("Log10 Shares Current")+
  ggtitle("C")+
  theme_bw(base_size=10)+
  theme(axis.line = element_line(colour = "darkgrey"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        legend.position="none",
        plot.title = element_text(lineheight=.8, face="bold", hjust = 0))

grid.arrange(l1,c1,s1, ncol=1)
```

## Correlation Analyses

```{r}
fb_corr <- fb_data %>%
  dplyr::select(Like.24, Share.24, Comment.24, Like.Current, Comment.Current,
         Share.Current)

M <- cor(fb_corr,use="complete.obs", method="spearman")
kable(M) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```
```{r}
rcorr(as.matrix(fb_corr), type="spearman") 
```
```{r}
quantile(fb_data$Percent.Likes, na.rm=TRUE)
quantile(fb_data$Like.24, na.rm=TRUE)

summary(fb_data$Percent.Comment)
summary(fb_data$Comment.24)
sum(fb_data$Comment.24 == 0)/76
sum(fb_data$Percent.Comment== 1, na.rm=TRUE)/(76-21)
quantile(fb_data$Percent.Comment, na.rm=TRUE)

summary(fb_data$Share.24)
sum(fb_data$Share.24 == 0)/76
summary(fb_data$Percent.Share)

```

```{r, warning=FALSE, message=FALSE}
l2 <- ggplot(fb_data, aes(log10(Like.24)))+
  geom_histogram(fill="#3b5998", color="black", alpha=.8)+
  theme_bw(base_size=10)+
  ylab(NULL)+
  xlab("Log10 Like at 24 hrs")+
  theme(axis.line = element_line(colour = "darkgrey"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        legend.position="none",
        plot.title = element_text(lineheight=.8, face="bold", hjust = 0))


c2 <- ggplot(fb_data, aes(log10(Comment.24)))+
  geom_histogram(fill="#BDBC89", color="black", alpha=.8)+
  theme_bw(base_size=10)+
  ylab("Number")+
  xlab("Log10 Comments at 24 hrs")+
  theme(axis.line = element_line(colour = "darkgrey"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        legend.position="none",
        plot.title = element_text(lineheight=.8, face="bold", hjust = 0))

s2 <- ggplot(fb_data, aes(log10(Share.24)))+
  geom_histogram(fill="#5B9A9B", color="black", alpha=.8)+
  theme_bw(base_size=10)+
  ylab(NULL)+
  xlab("Log10 Shares at 24 hrs")+
  theme(axis.line = element_line(colour = "darkgrey"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        legend.position="none",
        plot.title = element_text(lineheight=.8, face="bold", hjust = 0))

l2b <- ggplot(fb_data, aes(x=Percent.Likes))+
  geom_histogram(fill="#3b5998", color="black", alpha=.8)+
  theme_bw(base_size=10)+
  ylab(NULL)+
  xlab("Percent of Likes in 24 hrs")+
  theme(axis.line = element_line(colour = "darkgrey"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        legend.position="none",
        plot.title = element_text(lineheight=.8, face="bold", hjust = 0))


c2b <- ggplot(fb_data, aes(x=Percent.Comment))+
  geom_histogram(fill="#BDBC89", color="black", alpha=.8)+
  theme_bw(base_size=10)+
  ylab(NULL)+
  xlab("Percent of Comments in 24 hrs")+
  theme(axis.line = element_line(colour = "darkgrey"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        legend.position="none",
        plot.title = element_text(lineheight=.8, face="bold", hjust = 0))

s2b <- ggplot(fb_data, aes(Percent.Share))+
  geom_histogram(fill="#5B9A9B", color="black", alpha=.8)+
  theme_bw(base_size=10)+
  ylab(NULL)+
  xlab("Percent of Shares in 24 hrs")+
  theme(axis.line = element_line(colour = "darkgrey"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        legend.position="none",
        plot.title = element_text(lineheight=.8, face="bold", hjust = 0))

grid.arrange(l2, l2b, c2, c2b, s2, s2b, ncol=2)

```

## Predicting Likes Analyses

```{r, warning=FALSE, messages=FALSE}
p1 <- ggplot(fb_data, aes(Awe.Factor,LogLikes))+
        geom_boxplot(fill="#3b5998", color="black", alpha=.8, notch=FALSE)+
        theme_bw(base_size=10)+
        theme(panel.grid.major = element_line(size = .2, color = "grey"))+
        xlab("Awe Factor")+
        ylab("Log10 Facebook Likes")+
        theme(axis.text.x = element_text(angle = 45, hjust = 1))

p2 <- ggplot(fb_data, aes(Photo.Type, LogLikes))+
        geom_boxplot(fill="#3b5998", color="black", alpha=.8, notch=FALSE)+
        theme_bw(base_size=10)+
        theme(panel.grid.major = element_line(size = .2, color = "grey"))+
        xlab("Photo Type")+
        ylab(NULL) +
        theme(axis.text.x = element_text(angle = 45, hjust = 1))

p3 <- ggplot(fb_data, aes(Caption.Type, LogLikes))+
        geom_boxplot(fill="#3b5998", color="black", alpha=.8, notch=FALSE)+
        theme_bw(base_size=10)+
        theme(panel.grid.major = element_line(size = .2, color = "grey"))+
        xlab("Caption Type")+
        ylab(NULL)+
        theme(axis.text.x = element_text(angle = 45, hjust = 1))


p4 <- ggplot(fb_data, aes(Taxa, LogLikes))+
        geom_boxplot(fill="#3b5998", color="black", alpha=.8, notch=FALSE)+
        theme_bw(base_size=10)+
        theme(panel.grid.major = element_line(size = .2, color = "grey"))+
        xlab("Taxa")+
        ylab("Log10 Facebook Likes")+
        theme(axis.text.x = element_text(angle = 45, hjust = 1))+
        scale_x_discrete(labels = wrap_format(15))
  
grid.arrange(p1,p2,p3,p4, layout_matrix = rbind(c(1, 2, 3),
                                                c(4, 4, 4)))
```

## Predicting Likes Analyses

```{r, warning=FALSE, messages=FALSE}
hist(fb_data$Like.24,breaks=50)
```
Count data so will need to use Poisson model and test for overdispersion
```{r}
like_model_poisson<-glm(data=fb_data, Like.24~
                     Caption.Type+
                     Taxa+
                     Photo.Type+
                     Awe.Factor+
                     Days+
                     Time+
                     LogCapCount, family=poisson)
dispersiontest(like_model_poisson,trafo=1)
```
Model is over diserpsed with p-value = 3.308e-08.  Proceeding with Negative binomial regression
```{r}
like_model_negbin = glm.nb(data=fb_data, Like.24~
                               Caption.Type+
                               Taxa+
                               Photo.Type+
                               Awe.Factor+
                               Days+
                               Time+
                               LogCapCount,
                    control = glm.control(maxit=10000))
  #anova
  Anova(like_model_negbin, 
        type="II", 
        test="LR")
  #pseudo r squared
  nagelkerke(like_model_negbin)
```
```{r}
 #comparisons and contrasts
  marginal_taxa = emmeans(like_model_negbin, ~ Taxa )

  kable(pairs(marginal_taxa, adjust="tukey"))  %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
  
  kable(cld(marginal_taxa,
      alpha   = 0.05, 
      Letters = letters,    ### Use lower-case letters for .group
      type    = "response", ### Report emmeans in orginal scale
      adjust =  "tukey"))  %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"))    
  
  marginal_photo = emmeans(like_model_negbin, ~ Photo.Type )
  
  kable(pairs(marginal_photo, adjust="tukey"))  %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
  
  kable(cld(marginal_photo,
      alpha   = 0.05, 
      Letters = letters,    ### Use lower-case letters for .group
      type    = "response", ### Report emmeans in orginal scale
      adjust =  "tukey")) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
  
  marginal_awe = emmeans(like_model_negbin, ~ Awe.Factor )
  
  kable(pairs(marginal_awe, adjust="tukey")) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
  
  kable(cld(marginal_awe,
      alpha   = 0.05, 
      Letters = letters,    ### Use lower-case letters for .group
      type    = "response", ### Report emmeans in orginal scale
      adjust =  "tukey")) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
  
```

## Reduced Model

```{r}
#examine a reduced model
  drop1(like_model_negbin, test="F")
  
  like_model_negbin2 = glm.nb(data=fb_data, Like.24~
                               Taxa+
                               Photo.Type+
                               Awe.Factor,
                             control = glm.control(maxit=10000))
  #anova
  Anova(like_model_negbin2, 
        type="II", 
        test="LR")
  #pseudo r squared
  nagelkerke(like_model_negbin2)
  
  AIC(like_model_negbin, like_model_negbin2)
```

## Predicting New Data

```{r}
  newdata1 <- data.frame(Taxa = "Cephalopod", Photo.Type="Color", Awe.Factor="High")
  temp <- predict(like_model_negbin2, newdata1, type = "response",se.fit = TRUE)
  newdata1$predicted <- temp$fit
  newdata1$se <-temp$se.fit
  newdata1$upr <- with(newdata1, predicted + (2 *se)) 
  newdata1$lwr <- with(newdata1, predicted - (2 *se)) 
  newdata1
```

## Predicting Shares Analyses

```{r, warning=FALSE, message=FALSE}  
hist(fb_data$Share.24,breaks=50)
  summary(fb_data$Share.24)
  sum(fb_data$Share.24 == 0)
```
Large number of zeros as well so will need a zero inflation model, Obivously not a Poisson model but will run to show overdispersion
```{r}
  share_model_poisson<-glm(data=fb_data, Share.24~
                            Caption.Type+
                            Taxa+
                            Photo.Type+
                            Awe.Factor+
                            Days+
                            Time+
                            LogCapCount, family=poisson)
  summary(share_model_poisson)
  
  #need to test for overdispersion
  dispersiontest(share_model_poisson,trafo=1)
```
Model is over-dispersed with p-value=0.005757. Proceeding with Negative binomical regerssion
```{r} 
        share_model_negbin = glm.nb(data=fb_data, Share.24~
                                   Caption.Type+
                                   Taxa+
                                   Photo.Type+
                                   Awe.Factor+
                                   Days+
                                   Time+
                                   LogCapCount,
                                 control = glm.control(maxit=10000))
          #dispersion test
          odTest(share_model_negbin) 
```
Because Zero-inflation runs two models on zeros and non-zeros particularly sensitive to number of states in independent variables.  Working to reduced taxa down to post hoc groups of social media performance.
```{r Reduced Taxa Share Anaysis}
fb_data <- fb_data %>%
  mutate(Taxa2 = dplyr::recode(Taxa, 
           Cephalopod = "Charismatic",
           Osteichthyes = "Charismatic",
           Medusozoa = "Charismatic",
           Arthropod = "Average",
           Anthozoa = "Average",
           Porifera = "Average",
           Nudibranch = "Average",
           Nematoda = "Average",
           Testudines = "Average",
           Polychaete = "Average",
           GastropodBivalve = "Low",
           Elasmobranch = "Low",
           Cetacea = "Low",
           Pinneped = "Low",
           Echinoderm = "Low"))
        summary(fb_data$Taxa2)

        share_model_zi3 <- zeroinfl(data=fb_data, Share.24~
                                       Photo.Type+
                                       Awe.Factor+
                                       Taxa2+
                                      Caption.Type,
                                     dist = "negbin")
         
         summary(share_model_zi3)
         #anova
         Anova(share_model_zi3, 
               type="II", 
               test="Chisq")
         
         #pseudo r squared
         nagelkerke(share_model_zi3)
```
Comparisons
```{r Share Compariosn with Reduced Taxa}
         #comparisons
         marginal_taxa_share = emmeans(share_model_zi3, ~ Taxa2 )
         
         kable(pairs(marginal_taxa_share, adjust="tukey")) %>%
           kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
         
         kable(cld(marginal_taxa_share,
             alpha   = 0.05, 
             Letters = letters,    ### Use lower-case letters for .group
             type    = "response", ### Report emmeans in orginal scale
             adjust =  "tukey")) %>%
           kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
         
         marginal_caption_share = emmeans(share_model_zi3, ~ Caption.Type )
         kable(pairs(marginal_caption_share, adjust="tukey")) %>%
           kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
         
         kable(cld(marginal_caption_share,
             alpha   = 0.05, 
             Letters = letters,    ### Use lower-case letters for .group
             type    = "response", ### Report emmeans in orginal scale
             adjust =  "tukey")) %>%
           kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
         
         marginal_awe_share = emmeans(share_model_zi3, ~ Awe.Factor )
         kable(pairs(marginal_awe_share, adjust="tukey"))%>%
           kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
         
         kable(cld(marginal_awe_share ,
             alpha   = 0.05, 
             Letters = letters,    ### Use lower-case letters for .group
             type    = "response", ### Report emmeans in orginal scale
             adjust =  "tukey")) %>%
           kable_styling(bootstrap_options = c("striped", "hover", "condensed"))    
         
         marginal_photo_share = emmeans(share_model_zi3, ~ Photo.Type )
         
         kable(pairs(marginal_photo_share, adjust="tukey")) %>%
           kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
         
         kable(cld(marginal_photo_share ,
             alpha   = 0.05, 
             Letters = letters,    ### Use lower-case letters for .group
             type    = "response", ### Report emmeans in orginal scale
             adjust =  "tukey"))%>%
           kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

## Predicting Shares Plots

```{r, warning=FALSE, message=FALSE}  
p1s <- ggplot(fb_data, aes(Awe.Factor,LogShares))+
    geom_boxplot(fill="#5B9A9B", color="black", alpha=.8, notch=FALSE)+
    theme_bw(base_size=10)+
    theme(panel.grid.major = element_line(size = .2, color = "grey"))+
    xlab("Awe Factor")+
    ylab("Log10 Facebook Shares")+
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
  
  p2s <- ggplot(fb_data, aes(Caption.Type, LogShares))+
    geom_boxplot(fill="#5B9A9B", color="black", alpha=.8, notch=FALSE)+
    theme_bw(base_size=10)+
    theme(panel.grid.major = element_line(size = .2, color = "grey"))+
    xlab("Caption Type")+
    ylab("Log10 Facebook Shares")+
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
  
  p4s <- ggplot(fb_data, aes(Taxa2, LogLikes))+
    geom_boxplot(fill="#5B9A9B", color="black", alpha=.8, notch=FALSE)+
    theme_bw(base_size=10)+
    theme(panel.grid.major = element_line(size = .2, color = "grey"))+
    xlab("Taxon Group")+
    ylab("Log10 Facebook Shares")+
    theme(axis.text.x = element_text(angle = 45, hjust = 1))+
    scale_x_discrete(labels = wrap_format(15))
  
  grid.arrange(p1s,p2s,p4s, ncol=1)
  
  
  
```

```{r}
pdf(file="figure4.pdf",width=8.5, height=11, useDingbats=FALSE)
par(mar=c(5,3,2,2)+0.1) #removes space from around edges of pdf
 grid.arrange(p1s,p2s,p4s, ncol=1)
dev.off()
```

## Predicting Comments

```{r, warning=FALSE, message=FALSE}  
hist(fb_data$Comment.24,breaks=50)
         summary(fb_data$Comment.24)
         sum(fb_data$Comment.24 == 0)
```
Heavily zero inflated so will need a zero infaltion model.  Although obviously inccored, Will run Poisson model to demonstrate overdisperson.
```{r} 
  
         comment_model_poisson<-glm(data=fb_data, Comment.24~
                                    Caption.Type+
                                    Taxa+
                                    Photo.Type+
                                    Awe.Factor+
                                    Days+
                                    Time+
                                    LogCapCount, family=poisson)
         summary(comment_model_poisson)
         
         #need to test for overdispersion
         dispersiontest(comment_model_poisson,trafo=1)
```
Model is over dispersed with p-value = 0.005344. Proceeding with zero-inflation Negative binomial regression
```{r}         
         comment_model_zi3 <- zeroinfl(data=fb_data, Comment.24~
                                       Photo.Type+
                                       Awe.Factor+
                                       Caption.Type+
                                       Taxa2,
                                     dist = "negbin")

         
         #anova
         summary(comment_model_zi3)
         Anova(comment_model_zi3, 
               type="II", 
               test="Chisq")
         
         #pseudo r squared
         nagelkerke(comment_model_zi3)
```
Comparisons
```{r}       
         #comparisons
         marginal_taxa_share = emmeans(comment_model_zi3, ~ Taxa2 )

         kable(pairs(marginal_taxa_share, adjust="tukey")) %>%
           kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
         kable(cld(marginal_taxa_share,
             alpha   = 0.05, 
             Letters = letters,    ### Use lower-case letters for .group
             type    = "response", ### Report emmeans in orginal scale
             adjust =  "tukey")) %>%
           kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
         
         marginal_awe_share = emmeans(comment_model_zi3, ~ Awe.Factor )
         
         kable(pairs(marginal_awe_share, adjust="tukey")) %>%
           kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
         
         kable(cld(marginal_awe_share ,
             alpha   = 0.05, 
             Letters = letters,    ### Use lower-case letters for .group
             type    = "response", ### Report emmeans in orginal scale
             adjust =  "tukey")) %>%
           kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
         
         marginal_photo_share = emmeans(comment_model_zi3, ~ Photo.Type )
         
         kable(pairs(marginal_photo_share, adjust="tukey")) %>%
           kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
         kable (cld(marginal_photo_share ,
             alpha   = 0.05, 
             Letters = letters,    ### Use lower-case letters for .group
             type    = "response", ### Report emmeans in orginal scale
             adjust =  "tukey")) %>%
           kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

## Predicting Comments Plots

```{r, warning=FALSE, message=FALSE}  
         ####plots
         p1c <- ggplot(fb_data, aes(Awe.Factor,LogComments))+
           geom_boxplot(fill="#BDBC89", color="black", alpha=.8, notch=FALSE)+
           theme_bw(base_size=10)+
           theme(panel.grid.major = element_line(size = .2, color = "grey"))+
           xlab("Awe Factor")+
           ylab("Log10 Facebook Comments")+
           theme(axis.text.x = element_text(angle = 45, hjust = 1))
         
         p2c <- ggplot(fb_data, aes(Photo.Type, LogComments))+
           geom_boxplot(fill="#BDBC89", color="black", alpha=.8, notch=FALSE)+
           theme_bw(base_size=10)+
           theme(panel.grid.major = element_line(size = .2, color = "grey"))+
           xlab("Photo Type")+
           ylab("Log10 Facebook Comments")+
           theme(axis.text.x = element_text(angle = 45, hjust = 1))
         
         p4c <- ggplot(fb_data, aes(Taxa2, LogComments))+
           geom_boxplot(fill="#BDBC89", color="black", alpha=.8, notch=FALSE)+
           theme_bw(base_size=10)+
           theme(panel.grid.major = element_line(size = .2, color = "grey"))+
           xlab("Taxon Group")+
           ylab("Log10 Facebook Comments")+
           theme(axis.text.x = element_text(angle = 45, hjust = 1))+
           scale_x_discrete(labels = wrap_format(15))

         grid.arrange(p1c,p2c,p4c, ncol=1)
```       

```{r}
pdf(file="figure5.pdf",width=8.5, height=11, useDingbats=FALSE)
par(mar=c(5,3,2,2)+0.1) #removes space from around edges of pdf
 grid.arrange(p1c,p2c,p4c, ncol=1)
dev.off()
```


## Favorite Taxa Summary Data

```{r}
setwd("~/Desktop/Facebook Paper/Facebook Experiment")
fav_taxa <- read.csv("favorite_taxa(DSN).csv")
kable(summary(fav_taxa$Taxa)) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

